`flippant` -- An `R` package for the automated  analysis of dithionite

### 2015-09-16 inst/manuscript/manuscript.rmd
Implement a structure compatible with "Bioinformatics";
Paraphrasing in first intro paragraph;

# Introduction
Scramblases are proteins mediating the mass-action driven equilibration of 
lipids between the sheets of lipid bilayers representing biological membranes
<CITE SOME REVIEW>. Indipendent of ATP or other energy equivalents they 
facilitate this ``flipping'' by providing a mechanism of transition through the 
hydrophobic environment of membranes to polar lipid head groups, thus 
reducing the massive energetic cost that process would carry otherwise <CITE 
ANANT HALF TIME>. While the underlying molecular mechanisms remain enigmatic 
<CITE SOMETHING>, and molecules supporting flipping processes as central as the 
equilibration of the ubiquitous phosphoglycerolipids across the membrane of the 
endoplasmic reticulum, where they are synthesized in the cytoplasmicfrom sheet, 
have yet to be identified <CITE SOMETHING>, there has been much recent progress 
in scramblase identification and characterization. Molecules shown to have 
scramblase activity include opsin/rhodopsin <CITE INDU, MIKE, BIRGIT>, X <CITE> 
and Y <CITE>.

>>>>

##Summary

##Availability and Implementation

##Contact
jog2030@qatar-med.cornell.edu

##Supplementary Information

# Introduction
Scramblases are proteins mediating the mass-action driven equilibration of 
lipids between the sheets of lipid bilayers representing biological membranes
<CITE SOME REVIEW>. Indipendent of energy equivalents such as ATP they 
facilitate this ``flipping'' by providing a mechanism of transition through the 
hydrophobic environment of membranes to polar lipid head groups, thus 
reducing the massive energetic cost that process would carry otherwise <CITE 
ANANT HALF TIME>. While the underlying molecular mechanisms remain enigmatic 
<CITE SOMETHING>, and molecules supporting flipping processes as central as the 
equilibration of the ubiquitous phosphoglycerolipids across the membrane of the 
endoplasmic reticulum, where they are synthesized in the cytoplasmic sheet, 
have yet to be identified <CITE SOMETHING>, there has been much recent progress 
in scramblase identification and characterization. Molecules shown to have 
scramblase activity include opsin/rhodopsin <CITE INDU, MIKE, BIRGIT>, X <CITE> 
and Y <CITE>.

#Main Features

#Case Study

#Conclusion

#Funding
J.G., R.J.C. and the Proteomics Core at WCMC-Q were supported by ``Biomedical 
#Acknowledgements
